---
title: "Linear Model With Prediction"
author: "Connor Rice"
output: 
  html_document:
    number_sections: false
    toc: true
    toc_depth: 5
date: "`r Sys.Date()`"    
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
require(knitr)
require(foreign)
install.packages("car")
require(car)

mydata <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)

```

```{r}
model1 <- lm(SIMS~ARM,data=mydata)
plot(SIMS~ARM,data=mydata)
abline(model1)
specificdata1 <- data.frame(GRIP = 94, ARM = 88)
predict(model1, specificdata1, interval="prediction")
cor(mydata$SIMS, mydata$ARM)
```

The 95% prediction interval for the prediction of SIMS by ARM at the specific value of GRIP=94 ARM=88, has a prediction range between -1.726209 and 3.138977 with a total prediction range of: 4.865186. This is the second smallest prediction range of any of the models, making it the second best predictor of the SIMS value at the given point of ARM = 88 and GRIP = 94.

```{r}
model2 <- lm(SIMS~GRIP,data=mydata)
plot(SIMS~GRIP,data=mydata, main= "SIMS vs GRIP")
abline(model2)
specificdata2 <- data.frame(GRIP = 94, ARM = 88)
predict(model2, specificdata2, interval="prediction")
```

The 95% prediction interval for the prediction of SIMS by GRIP at the specific value of GRIP=94 ARM=88, has a prediction range between -3.107961 and 2.035652 with a total prediction range of: 5.143613. This is the largest prediction range of any of the models, making it the worst predictor of the SIMS value at the given point of ARM = 88 and GRIP = 94.

```{r}
model3 <- lm(SIMS~ARM + GRIP,data=mydata)
avPlots(model3)
specificdata3 <- data.frame(GRIP = 94, ARM = 88)
predict(model3, specificdata3, interval="prediction")
cor(mydata$SIMS~mydata$ARM + GRIP)
```

The 95% prediction interval for the prediction of SIMS by the combination of ARMS and GRIP at the specific value of GRIP=94 ARM=88, has a prediction range between -2.132373 and 2.431668 with a total prediction range of: 4.564041. This is the smallest prediction range of any of the models, making it the best predictor of the SIMS value at the given point of ARM = 88 and GRIP = 94.

```{r}
anova(model1,model3)
```


